\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-24 draft.tex
Section 5

J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1. We
run J-ReCoVer on a virtual machine with 4GB of memory running Ubuntu 16.04.5 LTS
on a server with AMD Opteron 6376 CPU.

\begin{wraptable}{r}{4cm}
	\vspace{-0.7cm}
	\caption{Size of the reducers.}
	\begin{tabular}{|c|c|c|c|}
		\hline
		& Line & Variable & Branch\\
		\hline
		Min. & 5 & 4 & 0\\
		Avg. & 20.5 & 14.7 & 1.2\\
		Max. & 58 & 37 & 5\\
		\hline
	\end{tabular}
	\label{tab:benchmark}
	\vspace{-0.5cm}
\end{wraptable}

@@

In order to properly evaluate the performance
of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java
programs containing the key strings ``public void reduce'' or ``protected void
reduce''. Since there is an upper bound on the number of results returned from
the search engine, we add different search filters in order to get more data. We
tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim
250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim
1250\}$ and two filters for data sources $\{\url{github.com},
\url{bitbuckect.com}\}$. In total, we get $11346$ Java programs. We exclude
cases that are not Hadoop MapReduce reducer programs (those do not import the
Hadoop library, do not extend or implement the reducer interface) and obtain
$1273$ examples. We further remove those that cannot be compiled, those that are
identical to each other, or those with non-numerical data types (e.g, string)
and obtained $118$ reducers as the final benchmarks. Figure~\ref{fig:benchmark}
contains the details of extracted reducer functions.

@@

J-ReCoVer successfully handled $115$ cases ($97.5\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool. Another $27\%$ of the execution time is in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations. The time spent in Solver is quite limited ($<1\%$), since the real-world integer reducer programs are usually not that big.

There is no other tool that could handle the reducers as they are. Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based back-end verifier (the Solver) turned out to work efficiently. So we did not feel a need to replace it by another verification tool. Of course, in the future, this can be done if need be.

J-ReCoVer fails in three cases because the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form of  $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$. In theory, such a program can be handled by more sophisticated program transformation tasks. For example, we can merge the two loops and push the outer branch condition into the merged loop.

>>>>

J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1. We
ran J-ReCoVer on a virtual machine with 4GB of memory running Ubuntu 16.04.5 LTS
on a server with AMD Opteron 6376 CPU.

\begin{wraptable}[7]{r}{40mm}
	\vspace{-8mm}
	\caption{Size of the reducers.}
	\begin{tabular}{|c|c|c|c|}
		\hline
		& Line & Variable & Branch\\
		\hline
		Min. & 5 & 4 & 0\\
		Avg. & 20.5 & 14.7 & 1.2\\
		Max. & 58 & 37 & 5\\
		\hline
	\end{tabular}
	\label{tab:benchmark}
	\vspace{-5mm}
\end{wraptable}

@@

In order to properly evaluate the performance of J-ReCoVer, we used the search
engine \emph{searchcode.com} to collect Java programs containing the key strings
``public void reduce'' or ``protected void reduce''. Since there is an upper
bound on the number of results returned from the search engine, we added
different search filters in order to get more data. We tried all $12$
combinations of six filters on the code length $\{<50$, $ 50\sim 250$, $250\sim
450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$ and two
filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$. In total,
we got $11,346$ Java programs. We excluded cases that were not Hadoop MapReduce
reducer programs (those do not import the Hadoop library, do not extend or
implement the reducer interface) and obtained $1,273$ examples. We further
removed those that could not be compiled, those that were identical to each
other, and those with non-numerical data types (e.g., strings). We obtained
$118$ reducers as the final benchmarks. Table~\ref{tab:benchmark} contains more
details of the considered reducer functions.

@@

J-ReCoVer successfully handled $115$ cases ($97.5~\%$) out of the considered
ones. The analysis time ranged between $9.8$ and $8.6$ seconds. On average,
$72~\%$ of the execution time was spent in compiling Java source code to
bytecode, which is the input of the Soot tool. Further, $27~\%$ of the execution
time was spent in the Preprocessor, in which Soot is used to transform Java
bytecode to Jimple and perform the program transformations. The time spent in
Solver is quite limited ($<1~\%$) since the real-world integer reducer programs
are usually not that big.

There is no other tool that could handle the reducers as they are. Perhaps some
other tools could be applied on the transformed programs, but the
transformations would still be needed, and our SMT-based back-end verifier (the
Solver) turned out to work efficiently. Hence, we did not feel a need to replace
it by another verification tool. Of course, in the future, this can be done if
need be.

J-ReCoVer failed in three cases out of the considered ones because the three
reducers use more complicated control structures than what J-ReCoVer currently
supports. Namely, they use a branch statement before entering the loop, i.e.,
they have the form of
$\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$. In theory, such
a program can be handled by more sophisticated program transformations. For
example, we can merge the two loops and push the outer branch condition into the
merged loop. Extensions of J-ReCoVer to be able to handle such constructions,
together with a support for more data types, belong among our future works.
